---
title: "FSB State Placement Dashboard"
author: "Elijah Weaver & Molly Wimer"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE,cache = TRUE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT,
               usmap,
               geojsonio,
               broom#for better tables
               )

#read in data
clean_data =readRDS("Cleaned_Survey_Data.RDS")
```

# Survey Overview {data-orientation=columns}

Overview of survey responses

## row {data-width=600}

### Where are students going?

We spoke with Michelle Chevalier, Director of Industry Partnerships for Farmer School of Business (FSB), to gain insights about how she picks locations to build corporate relationships with for FSB students. Historically, it was believed that most FSB graduates accepted jobs in "The 4-C's": Cincinnati, Columbus, Cleveland, and Chicago. Naturally, FSB dedicates many resources to building relationships with companies in these cities. Our hypothesis is that students are still accepting jobs in the 4 C's, but there is also a business case to expand to other cities. Michelle stated that in her role, she has to consider preferred locations from students as well as look at industry trends to predict where students will be heading the future. Furthermore, she said another pain she faces in her role is that "If I only know of 10 students who want to live in Houston, TX, and those 10 students are spread across 3 majors, it's hard to make the case to a company to spend their time and money engaging with Miami for just a few students". After considering this, our analysis will also include major specific analysis for each of the cities we are proposing. Using historical FSB grad data, we will provide Michelle with a list of cities where there is a high number of students within the same major that have moved to this city.

### Why does this matter?

If we just rely on the historical precedent that most students are going to the 4 C's after graduation, we could be missing a large population of students that are going to other cities. These students may not feel supported by the university which would reflect badly upon FSB and it's ability to place students in their preferred roles. For example, if a student is from the Northeast region of the US and wants to study at FSB, but hears that grads are only placed in the 4 C's and they want to return to the Northeast post-grad, they might pick another university that places students all over the US. Out-of-state students have historically made up 40% of Miami's student body, meaning that these students are critical to ensure the future of the university.

### Number of Responses

```{r,echo=FALSE}
nusable = nrow(clean_data)
valueBox(nusable, icon = "fa-users")
```   
   
## row {data-width=400}

### Student State Repsonse Rate

```{r, echo = FALSE}
rate <- round(100*sum(!is.na(clean_data$survey_state)) / nrow(clean_data), 0)
gauge(rate, min = 0, max = 100,symbol = '%',
      gaugeSectors(success = c(80,100), warning = c(40,79), danger = c(0,39)
        )
      )
```

### Preferred location

```{r, echo = FALSE}
rate1 <- round(100*sum(clean_data$survey_pref_loc == 1, na.rm = TRUE)/sum(!is.na(clean_data$survey_pref_loc)), 0)
gauge(rate1, min = 0, max = 100,symbol = '%',
      gaugeSectors(success = c(80,100), warning = c(40,79), danger = c(0,39)
        )
      )
```


### Student Majors

```{r, echo = FALSE}
p <- ggplot(clean_data, aes(x = reorder(major1, major1, function(x) -length(x)))) +
  geom_bar(color = "steelblue", fill = "steelblue") +
  xlab("Primary Major") +
  ylab("Number of Responses") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust = 10, hjust = 10, angle = 90)) 
ggplotly(p)
```

# Student by State {data-orientation=columns}

## Column {data-width=600}

### Cloropleth

```{r,echo=FALSE}
state_counts <- as.data.frame(table(clean_data$survey_state))
colnames(state_counts) <- c("state", "Count")
state_counts <- subset(state_counts, nchar(as.character(state)) <= 2)
state_counts <- state_counts[!state_counts$state %in% c("OH", "IL"), ]

plot_usmap(data = state_counts, values = "Count", color = "black") + 
  scale_fill_continuous(name = "Population (2015)", label = scales::comma) + 
  theme(legend.position = "right")
```

### Table of Student States

```{r,echo=FALSE}
data1 <- clean_data %>% 
  filter(!is.na(survey_state)) %>% 
  group_by(survey_state) %>%
  summarize(count=n())

datatable(data1,rownames=F,extensions='Buttons',
          options=list(dom='Bfrtip',
                       buttons = c("copy","csv","excel")
                       ),
          filter=list(position='bottom',
                      clear=F,plain=T
                      )
          )
```

# Major By City {data-orientation=columns}

## Column {data-width=400}

### Overall bar chart of states with greater than 5 people

```{r, echo=FALSE}
cleaner_data <- subset(clean_data, nchar(as.character(survey_state)) <= 2)
cleaner_data <- clean_data[clean_data$survey_state %in% names(which(table(clean_data$survey_state) >= 5)), ]

p <- ggplot(cleaner_data, aes(x = reorder(survey_state, survey_state, function(x) -length(x)))) +
  geom_bar(color = "steelblue", fill = "steelblue") +
  xlab("State") +
  ylab("Number of Responses") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust = 10, hjust = 10, angle = 90)) 
ggplotly(p)
```

### Overall bar chart of cities with greater than 10 people 

```{r,echo=FALSE}
df_filtered <- clean_data[clean_data$survey_city %in% names(which(table(clean_data$survey_city) >= 10)), ]

p <- ggplot(df_filtered, aes(x = reorder(survey_city, survey_city, function(x) -length(x)))) +
  geom_bar(color = "steelblue", fill = "steelblue") +
  xlab("City") +
  ylab("Number of Responses") +
  theme_bw() +
  theme(axis.text.x = element_text(vjust = 10, hjust = 10, angle = 90)) 
ggplotly(p)
```

## Column {data-width=600}

### City Table 

```{r,echo=FALSE}
data <- clean_data %>% 
  filter(!is.na(survey_city)) %>% 
  group_by(survey_city,survey_state,major1) %>%
  summarize(count=n()) %>% 
  arrange(major1,-count)

datatable(data,rownames=F,extensions='Buttons',
          options=list(dom='Bfrtip',
                       buttons = c("copy","csv","excel")
                       ),
          filter=list(position='bottom',
                      clear=F,plain=T
                      )
          )
```

# Analysis {data-orientation=columns}

For each page of the dashboard, we will explore what information they provide towards our analysis.

## Column {data-width=600}

### Survey Overview

The survey overview page gives us general information that will be useful in this analysis. The text boxes help explain our customer and the current pains they are experiencing which our solution aims to address. The gauges inform us that 60% of students responded to this survey for a total of 3235 responses. Furthermore, we learn that 92% of students have jobs in their preferred location which means that this data can mostly be generalized about where students want to be after graduation. Finally, we see a breakdown of how many students are in each major in this data set. Finance, marketing, and accounting have the highest numbers. Our analysis will be most informative for people in this major because we have more data to work with. 

### Student by State

This chloropleth is the first deliverable for the customer. Since our goal was to analyze where students are going outside of the "4 C's", we excluded Ohio and Illinois from this map. States with a lighter blue color have more FSB graduates than states with a navy color. Gray states had no students there. This map is our first indication that states like New York, California, and Indiana have a high count of students also going there. The table below the chloropleth can be used to get exact counts of where students are going to that state. We will dig into this analysis deeper on the Major by City page. 

### Major by City

The bar chart of states with more than 5 people reiterates the information from the Student by State page, but includes Ohio and Illinois to show the relative amount of students going to each state. Below, the bar chart of cities with more than 10 people, can give Michelle an indication of what cities might be worth exploring to build corporate relationships. For example, after the 4 C's, the cities with the next highest counts are New York City, Indianapolis, Denver, and Boston. The bar chart supports the fact that most FSB grads are going to the 4 C's, but other cities also have high value counts that are not too far behind the 4 C's. You can then move to the table to explore the data by city. For example, if you type 'New York City' into the filter, you can see that 33 finance majors and 20 marketing majors are going to these cities. Michelle could focus her corporate relationships on finance firms or marketing agencies in New York City. Majors like accounting and supply chain have 6 or less people, so they might not be worth exploring corporate relationships. Similarly, Charlotte has a high concentration of finance majors with 8 people in our data set going there. During our initial interview, Michelle stated that there has been increasing desire to move to Charlotte recently for finance roles, so the data supports this claim. By inspecting count of each major in each city, Michelle can pick which cities to focus building corporate relationships with.
