---
title: "FSB State Placement Dashboard"
author: "Elijah Weaver & Molly Wimer"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE,cache = TRUE)

#package intialization
if(require(pacman)==FALSE) install.packages("pacman")
pacman::p_load(tidyverse, #for data manipulation
               plotly, #for interactive plots
               flexdashboard, #to make a dashboard
               fontawesome, #for icons
               DT #for better tables
               )

#read in data
internraw=readRDS("FSB_BI_Survey_2019_2021.rds")
```

# Survey Overview {data-orientation=columns}

Overview of survey responses

## row {data-width=700}

### Where are students going?

We spoke with Michelle Chevalier, Director of Industry Partnerships for Farmer School of Business (FSB), to gain insights about how she picks locations to build corporate relationships with for FSB students. Historically, it was believed that most FSB graduates accepted jobs in "The 4-C's": Cincinnati, Columbus, Cleveland, and Chicago. Naturally, FSB dedicates many resources to building relationships with companies in these cities. Our hypothesis is that students are still accepting jobs in the 4 C's, but there is also a business case to expand to other cities. Michelle stated that in her role, she has to consider preferred locations from students as well as look at industry trends to predict where students will be heading the future. Furthermore, she said another pain she faces in her role is that "If I only know of 10 students who want to live in Houston, TX, and those 10 students are spread across 3 majors, it's hard to make the case to a company to spend their time and money engaging with Miami for just a few students". After considering this, our analysis will also include major specific analysis for each of the cities we are proposing. Using historical FSB grad data, we will provide Michelle with a list of cities where there is a high number of students within the same major that have moved to this city.

### Why does this matter?

If we just rely on the historical precedent that most students are going to the 4 C's after graduation, we could be missing a large population of students that are going to other cities. These students may not feel supported by the university which would reflect badly upon FSB and it's ability to place students in their preferred roles. For example, if a student is from the Northeast region of the US and wants to study at FSB, but hears that grads are only placed in the 4 C's and they want to return to the Northeast post-grad, they might pick another university that places students all over the US. Out-of-state students have historically made up 40% of Miami's student body, meaning that these students are critical to ensure the future of the university.

```{r,echo=FALSE}

```
   
   
## row {data-width=300}

### Student State Repsonse Rate

```{r, echo = FALSE}
rate <- round(100*sum(!is.na(df$survey_state)) / nrow(df), 0)
gauge(rate, min = 0, max = 100,symbol = '%',
      gaugeSectors(success = c(80,100), warning = c(40,79), danger = c(0,39)
        )
      )
```

### Preferred location

```{r, echo = FALSE}
rate <- round(100*sum(df$survey_pref_loc=="Yes")/nrow(df),0)
gauge(rate, min = 0, max = 100,symbol = '%',
      gaugeSectors(success = c(80,100), warning = c(40,79), danger = c(0,39)
        )
      )
```


### Number of Responses

```{r,echo=FALSE}
nusable = nrow(df)
valueBox(nusable, icon = "fa-users")
```   


# Internships by Majors {data-orientation=columns}

## Column {data-height=800}

### Cloropleth

Chloropleth showing the us with number of student in each state post graduation represnted by a color scale

```{r,echo=FALSE}

```


### Filter {data-height=200}

Be able to filter by major and also by region

# Major By City {data-orientation=columns}

## Column {data-width=700}

### Cities with over 10 people 

Bar chart of major by city that is filterable below by different cities

### Filter by City {data-height=200}

```{r,echo=FALSE}

```

## Column {data-width=300}

### Overall bar chart of states

```{r}

```

### Overall bar chart of cities

```{r}

```

